A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-13 paper/paper.tex
Fixed prm
rearranged algorithms
writing upr esults

\section{Background}

@@

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in
which a roadmap is constructed by sampling random points in the C-space, and
the query phase in which a graph search over the roadmap is made to connect
initial and goal configurations \cite{kavraki1996prm}. The map is constructed
during the preprocessing phase by sampling random points in the C-space and
then adding them to the vertices in the roadmap within a certain radius of the
point. The algorithm is described in Alg~\ref{alg:PRM}.
%PRM can be elevated to the asymptotically optimal PRM*, which is
%described in Alg~\ref{alg:PRMstar}, by defining the radius to be a function of
%the number of vertices and the dimensionality of the space
%\cite{karaman2011sampling}. Since PRM* is asymptotically optimal, its solution
%will converge to the optimal path as time goes to infinity.

@@

The Rapidly exploring Random Tree algorithm works by building up a tree from
the initial configuration to the goal configuration \cite{lavalle1998rrt}.
Starting with the initial configuration as the root, it incrementally attempts
to add randomly selected samples to the tree until it reaches the goal
configuration.  The tree is ``rapidly exploring'' because the sample selection
is biased towards areas with large Voronoi regions (where the Voronoi regions
are computed based off of the nodes of the tree). RRTConnect, which is
described in Algos.~\ref{alg:extend_RRT},~\ref{alg:connect_RRT},
and~\ref{alg:RRTConnect}, differs from RRT in that two trees, one with its root
at the initial configuration and one with its root at the start configuration,
grow towards each other \cite{kuffner2000rrt}.
%RRT*, which is described in Alg~\ref{alg:RRTstar} differs from RRT in that for every new node, connections are tested to the new node from every other node that is within a certain radius from the new node \cite{karaman2011sampling}. The the tree is pruned so that edges that are not part of the shortest path from the root of the tree to the new node are removed.

@@

\begin{figure}[h!]
    \centering
    \makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{plots}}
    \caption{Figure}
\end{figure}

You can see examples of our code running in Fig.~\ref{fig:examples}. The
results are listed in Figure WHAT. They show that

\begin{algorithm}[ht] 
    \caption{$\Function{PRM}~\cite{karaman2011sampling}}
    \label{alg:PRM}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{\Var{init}}\} \cup \{\Var{SampleFree}_i\}_{i=1,\ldots,n}$
        \STATE $E \leftarrow \emptyset$
        \FORALL{$v \in V$}
            \STATE $U \leftarrow \Function{Near}(G = (V, E), x_{rand}, r);$
            \STATE $ V \leftarrow V \cup {x_{rand}} $
            \FORALL{$u \in U $}
                \IF{$\Function{CollisionFree}(v, u)$}
                    \STATE $E \leftarrow E \cup \{(v, u), (u, v)\}$
                \ENDIF
            \ENDFOR
        \ENDFOR
        \RETURN $G = (V, E)$

>>>>

\section{Introduction}

@@

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in
which a roadmap is constructed by sampling random points in the C-space, and
the query phase in which a graph search over the roadmap is made to connect
initial and goal configurations \cite{kavraki1996prm}. The map is constructed
during the preprocessing phase by sampling random points in the C-space and
then adding them to the vertices in the roadmap within a certain radius of the
point. The algorithm is described in Alg~\ref{alg:PRM}.

@@

The Rapidly exploring Random Tree algorithm works by building up a tree from
the initial configuration to the goal configuration \cite{lavalle1998rrt}.
Starting with the initial configuration as the root, it incrementally attempts
to add randomly selected samples to the tree until it reaches the goal
configuration.  The tree is ``rapidly exploring'' because the sample selection
is biased towards areas with large Voronoi regions (where the Voronoi regions
are computed based off of the nodes of the tree). RRTConnect, which is
described in Algos.~\ref{alg:extend_RRT},~\ref{alg:connect_RRT},
and~\ref{alg:RRTConnect}, differs from RRT in that two trees, one with its root
at the initial configuration and one with its root at the start configuration,
grow towards each other \cite{kuffner2000rrt}.

@@

\begin{figure}[h!]
    \centering
    \makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{plots}}

    \caption{Plots showing the length of the solution paths if found, the
    time needed to find the solution, and the number of failed attempts out of
    100 for each method of dimensionality reduction as well as in the high
    dimensional space. The column of plots on the left shows the results for
    the RRTConnect algorithm and the plots on the right show the results for
PRM. Note, The Y-axes limits are not equal and that abbreviations were used to
save space.  F.  Agg.  stands for Feature Agglomeration and R. PCA stands for
Randomized PCA.}

    \label{fig:plots}

\end{figure}

Fig.~\ref{fig:plots} shows plots of various measures of performance using
different methods of dimensionality reduction for motion planing. The left and
right columns show the results for RRTConnect and PRM algorithms respectively.
The first, second, and third row show the average path length, computational
time in seconds, and number of failed runs out of 100 respectively. For each
dimensionality reduction technique, there are three bars presenting the results
for 250, 300, and 350 randomly generated obstacles respectively. From the data
we can see that both planners produced similarly sized paths for each
dimensionality reduction technique, and that by not reducing the dimension, the
planner is able to find a path roughly two times shorter.

In terms of computational time, there is no significant difference between
Truncated SVD, PCA, Randomized PCA, planning in the original space when
planning with the RRTConnect algorithm. Whereas using Feature Agglomeration
took slightly longer to compute for each set number of obstacles. When using
PRM, the computational time was significantly improved by reducing the
dimension for all methods.  Based on the data, using PRM without dimensionality
reduction took roughly twice as long to compute for each method. This differing
result between PRM and RRTConnect is likely due to the fact that PRM is a
multi-query planning algorithm meaning that it constructs a data-structure that
can be used for multiple planning queries whereas RRTConnect is only looking to
find a single path. This means that the PRM algorithm tries to fully represent
the connectivity of the environment whilst RRTConnect needs to determine the
connectivity directed towards a goal. The reason dimensionality reduction
significantly improves the computational time for PRM is that it is much faster
to exhaust the search space at lower dimensions as opposed to higher
dimensions.

The RRTConnect algorithm had a much lower failure rate than PRM in all
respective dimensionality reduction technique. This is due to the fact that
RRTConnect is growing a tree towards the goal and PRM is randomly sampling and
connecting points to a growing graph. For both algorithms, a similar trend
exists for failure rate for planning in the reduced dimension space.

\begin{algorithm}[ht] 
    \caption{$\Function{PRM}$~\cite{karaman2011sampling}}
    \label{alg:PRM}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{\Var{init}}\} \cup \{\Var{SampleFree}_i\}_{i=1,\ldots,n}$
        \STATE $E \leftarrow \emptyset$
        \FORALL{$v \in V$}
            \STATE $U \leftarrow \Function{NearestNeighbors}(v)$
            \FORALL{$u \in U $}
                \IF{$\Function{CollisionFree}(v, u)$}
                    \STATE $E \leftarrow E \cup \{(v, u), (u, v)\}$
                \ENDIF
            \ENDFOR
        \ENDFOR
        \RETURN $G = (V, E)$
